Fusing Filters with Integer Linear Programming

### 2014-05-12 2014betterfusionforfilters/section/04-ILP.tex
ilp: different sizes: why fusing different sized arrays if important

The main difference to existing integer linear programming solutions is that, while nodes with different loop sizes cannot generally be fused together, we do support some fusion of filtered sizes. If two nodes have different sizes or rates, but are both sub-rates of another rate, they \emph{can} be fused together if they are both fused with their generators. \ben{What is a subrate? How do we determine the subrates of each rate?} \ben{Highlight why we want to allow this sort of fusion, and why it is specific to data flow fusion.} \ben{Explain how we are using the idea of transducers}.

>>>>

This is the main difference to existing integer linear programming solutions: we allow nodes with different iteration sizes to be fused together, when their parent transducers are fused together.
This is an important feature for combinator-based programming, where size-changing operations such as @filter@ are used frequently.
\ben{Highlight why we want to allow this sort of fusion, and why it is specific to data flow fusion.}
